Using Scipion for Stream Image Processing at EM Facilities

### 2018-03-22 6.acknowledgments.tex
go home

UPDATE THIS acknowledgments

Javier Vargas is the recipient of a ‘‘Comfuturo” grant funded by
the Fundación General CSIC, C.O.S. Sorzano is the recipient of a
Ramón y Cajal fellowship from the Spanish Ministry of Economy
and Competitiveness (MINECO). The authors acknowledge financial
support from the MINECO through Grants AIC-A-2011-0638,
BFU2013-41249-P and BIO2013-44647-R, the Comunidad de
Madrid through Grant CAM (S2010/BMD-2305), the European
Union (EU) and Horizon 2020 through Grants EINFRA-2014-2:
EGI Engage (Proposal: 654142) and EINFRA-2015-1: West-Life
(Proposal: 675858).
This work was partially funded by Instruct, a component of the
European Strategy Forum on Research Infrastructures (ESFRI), and
supported by national member subscriptions.

>>>>

The authors would like to acknowledge economical support from:
The Spanish Ministry of Economy and Competitiveness through Grants BIO2013-44647-R, BIO2016-76400-R(AEI/FEDER, UE) and AEI/FEDER BFU 2016 74868P, the Comunidad Aut\'{o}noma de Madrid through Grant: S2017/BMD-3817, European Union (EU) and Horizon 2020 through grant CORBEL (INFRADEV-1-2014-1, Proposal: 654248). This work used the EGI Infrastructure and is co-funded by the EGI-Engage project (Horizon 2020) under Grant number 654142. European Union (EU) and Horizon 2020 through grant West-Life (EINFRA-2015-1, Proposal: 675858) European Union (EU) and Horizon 2020 through grant Elixir - EXCELERATE (INFRADEV-3-2015, Proposal: 676559) European Union (EU) and Horizon 2020 through grant iNEXT (INFRAIA-1-2014-2015, Proposal: 653706). The authors acknowledge the support and the use of resources of Instruct, a Landmark ESFRI project.
